---
title: "A UN Report on the relationship between GDP and Life Expectancy"
author: "Amanda Photenhauer"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)##contains ggplot package
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

#My Plot

```{r gdp_lifeexp_1997}
ggplot(data = gapminder_1997, aes(x = gdpPercap, y = lifeExp, color=continent)) +
  labs(x = "GDP Per Capita", y = "Life Expectancy", 
       size = "Population (in Millions", title = "Do people in wealthy countries live longer?")+
  geom_point()+
  scale_color_brewer(palette = "Set1")
```

```{r data_summary, include=FALSE}

  nCountries <- length(unique(gapminder_1997$country)) 

  minGDP <- round(min(gapminder_1997$gdpPercap), digits=0) 

  maxGDP <- round(max(gapminder_1997$gdpPercap), digits=0)
```

The above plot shows the relationship between GDP per capita and life expectancy 
for a total of `r nCountries` countries. For this set of countries, 
economic wealth ranged from a minimum of USD `r minGDP`
to a maximum of USD `r maxGDP` per capita.

# Introduction

### Exercise
<ul>
 1. HTML
 1. <i>ggplot()</i>
 1. <b><i>HKL3000 download</i></b>
 *<a href="https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf">R Cheatsheet</a>
</ul>